\section{Work Experience}

% entry type must contain 4 arguments or it will FAIL
\entry{Network Security Engineer}
{Trend Micro}
{Nov 2021 - Present}
{}

\begin{itemize}
  \item \subsection*{\textbf{Project: Home Network Security(HNS SDK)}}
    \begin{itemize}
        \setlength\topsep{0em}
        \setlength\parskip{0em}
        \setlength\parsep{0em}
        \setlength\itemsep{0em}
      \item Ported HNS SDK to embedded home router device
      \item Familier with netfilter framework like iptables, nfqueue, conntrack
      \item Acquire basic networking based issues solving techniques like tcpdump, wireshark
      \item Debugged with gdb
      \item Successfully resolved issues that resulted in significant improvements over the previous year.
      \item Made remarkable contributions, including bug fixes and enhancements, enhancing the team's productivity and project quality.
      \item Collaborated effectively with other teams and made valuable contributions.
      \item Demonstrated the ability to identify root causes of complex problems, improving troubleshooting and decision-making.
      \item Played a pivotal role in fixing issues in the UFWD deinitialization process within the QTnet project.
      \item Resolved conflicts between VP detection and ISC scan, ensuring seamless operation in QTnet.
      \item Solved critical core crashes in the integration of ISC into the solution, working closely with ISC developers.
      \item Implemented workarounds and resolved initialization issues with ISC, improving the stability of the solution.
      \item Investigated and improved UFWD to prevent UDP packet issues and DNS query delays.
      \item Collaborated with Ramesh to identify and solve issues related to nfqueue limitations and DNS query delays.
      \item Committed valuable contributions to the master branch for the benefit of other projects, including bug fixes and enhancements.
      \item Addressed compile errors and improved error control.
      \item Demonstrated resourcefulness in overcoming challenges and limitations, creating workarounds for missing commands and resources.
      \item Adapted to cross-compilation and software development tools.
      \item Managed individual tasks efficiently when necessary.
      \item Actively contributed to problem-solving, including overcoming equipment and testing limitations with creative solutions.
    \end{itemize}
\end{itemize}


